A dynamic programing algorithm to assess the reliability of inferences from network enrichment analysis

### 2018-04-30 doc/genesetdp.tex
x

Here, we wanted to determine a full score distribution, {\em i.e.} the number of ways, $N(s)$, we can pick $Q$ genes and obtaining a score, $s$. This allows us to evaluate our score against the null hyptesis, $H_0$ : ``The Q query genes are randomly selected from the genes in the genome''. This can be expressed as an unbiased empirical $p$~value for obtaining a score $s$,

\begin{equation}
p(s)=\frac{N(s)/2 +\sum_{s'=s+1}^{S} N(s')}{\sum_{s'=0}^{S} N(s')},
\label{eq:pval}
\end{equation}
where $S$ is the maximal score.

>>>>

Here, we wanted to determine a full score distribution, {\em i.e.} the number of ways, $N(s)$, we can pick $Q$ genes and obtaining a score, $s$. This allows us to evaluate our score against the null hyptesis, $H_0$ : ``The Q query genes are randomly selected from the genes in the genome''. This can be expressed as a mid $p$~value\cite{lancaster1961significance,hwang2001optimality} for obtaining a score $s$,

\begin{equation}
p(s)=\frac{N(s)/2 +\sum_{s'=s+1}^{S} N(s')}{\sum_{s'=0}^{S} N(s')},
\label{eq:pval}
\end{equation}
where $S$ is the maximal score $s$ that $Q$ genes can obtain from Equation \ref{eq:sum_ij}.
